Capstone Movielens Report

### 2025-05-05 reports/capstone-movielens-report.draft4.tex
Draft RMD report updated.

\subparagraph{Movie Genres Data}\label{movie-genres-data}

\hfill\break
The following code computes movie rating summaries by popular genres
like Drama, Comedy, Thriller, and Romance:

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-16-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-31-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-37-1.pdf}
Now we can determine the minimal \emph{RMSE}:

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
Below are worst and best ratings categories:

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}

>>>>

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-29-1.pdf}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-36-1.pdf}
Now we can determine the minimal \emph{RMSE}:

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-42-1.pdf}

@@

\paragraph{Genre Data Analysis}\label{genre-data-analysis}

\hfill\break
\#\#\#\#\# Movie Genres Data\\
The following code computes movie rating summaries by popular genres
like Drama, Comedy, Thriller, and Romance:

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}

\subparagraph{Movie Genres Effect}\label{movie-genres-effect}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-48-1.pdf}
Below are worst and best ratings categories:

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-50-1.pdf}
